formula1

### 2019-12-23 inst/formula1.Rmd
slight tweak
rank not order

m <- maxp(L2017)
ox <- order(points,decreasing=TRUE)
oy <- order(m,decreasing=TRUE)
par(pty='s') # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,25),ylim=c(0,25),pch=16,
xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE) # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(m)[ox[i]],pos=4,col='gray') }
par(xpd=FALSE) # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

In the graph above, we see that both systems consider Hamilton to be
the best.  However, F1 points place Vettel second and Bottas third,
while `hyper2` places Bottas second and Vettel third.  Overall, there
is a high degree of correlation between the two, but differences in
detail.

@@

(mallyears <- maxp(F1_total))
```

@@

>>>>

m <- maxp(L2017)
ox <- rank(-points)
oy <- rank(-m)
par(pty='s') # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,25),ylim=c(0,25),pch=16,
xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE) # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(m)[ox[i]],pos=4,col='gray') }
par(xpd=FALSE) # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

In the graph above, we see a certain amount of disagreement.  
For example, using F1 points scored places Hamilton first and Vettel
second; while `hyper2` places Vettel first and Hamilton second.  But
overall there seems to be some degree of correlation between the two,
and differences in detail.

@@

mallyears <- maxp(F1_total)
```

@@

We see that Hamilton has the highest estimated strength.
